---
title: "Task 1"
author: "Ariella Fuzaylov and Candice Djorno"
date: "4/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(tidyverse)
library(survey)
library(srvyr)
```


```{r load data}
Employee_A_data=read.csv("Employee_A_data.csv", header=TRUE)
```

# Given

- Population of $N = 40,041$ reviews
- Employee A took an SRS of $n = 6,000$ reviews

## Subtask 1:

### Estimate average rating

Under SRSWOR, the sample mean $\bar{y} = \frac{1}{n}\sum_{i\in S}{y_i}$ is an unbiased estimator for the population mean $\hat{\mu}$.

```{r}
N = 40041
n= 6000
y_bar<-sum(Employee_A_data$Rating)/n
```

Thus, the estimated average rating is $\hat{\mu}=$ `r y_bar`.

## Confidence interval
```{r}
srs_design = svydesign(id=~1,data=Employee_A_data, fpc=rep(N,n))
svymean(x=~Rating,design = srs_design)
conf= confint(svymean(x=~Rating,design = srs_design))
conf
```

A 95% confidence interval is [`r conf[1]`, `r conf[2]`].

## Subtask 2

### Calculate Mean by Branch

```{r test}
rating.summary<-Employee_A_data%>%
  summarise(n= n(), Mean= mean(Rating),Var=sd(Rating)^2)
knitr::kable(rating.summary, caption = "Rating Summary Statistics")

rating.summary.by.branch<-Employee_A_data%>% group_by(Branch)%>%
  summarise(n= n(), Mean= mean(Rating),StD=sd(Rating))
knitr::kable(rating.summary.by.branch, caption = "Rating Summarised by Branch")



```

The estimated average rating for California is 4.396533, for Hong Kong is 4.213475, for Paris is 3.976963.

### Hypothesis Test
 
We perform a hypothesis test to determine whether there is evidence that any of the ratings are statistically significantly different from each other in the population.

$H_0 : {\mu}_{california}={\mu}_{hongkong}={\mu}_{paris}$

$H_1 : {\mu}_{california}\neq{\mu}_{hongkong}$ or ${\mu}_{california}\neq{\mu}_{paris}$ or 
${\mu}_{hongkong}\neq{\mu}_{paris}$ (i.e. the means are not all equal).

We perform an ANOVA.

```{r}
rating_aov = aov(Rating~Branch,data=Employee_A_data)
summary(rating_aov)
```

We obtain $p-value < 2e-16$ so $p-value < \alpha$. Therefore, we reject the null hypothesis and we conclude that there is evidence that Employee A could achieve more precision for these estimates.

