---
title: "Task 3"
author: "Ariella Fuzaylov and Candice Djorno"
date: "4/3/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(ggplot2)
# library(tidyverse)
library(sampling)
library(survey)
library(srvyr)
```

We transform the data Employee_B_probs into a matrix.

```{r load data}
Employee.B.Branch=read.csv("Employee_B_by_Branch.csv", header=TRUE)
Employee.B.overall=read.csv("Employee_B_overall.csv", header=TRUE)
Employee.B.probs=as.matrix(read.csv("Employee_B_probs.csv", header=FALSE))
```

We add col and row names for human readability. 

```{r test}
head(Employee.B.Branch)
head(Employee.B.overall)

month<-Employee.B.overall$Year_Month

colnames(Employee.B.probs)<-month
rownames(Employee.B.probs)<-month

Employee.B.probs
```

## Subtask 1

### Estimate average rating

```{r test}
my_design<-svydesign(id=~Year_Month,prob=~diag(Employee.B.probs),
                     fpc=~rep(15/112,15),
                     data=Employee.B.overall, 
                     pps=ppsmat(Employee.B.probs))
svymean(~Total_of_Ratings,my_design)
```

The estimated average satisfaction rating overall for the population of 40,041 reviews is 4.2182.

### Confidence interval

```{r}
conf= confint(svymean(x=~Total_of_Ratings,design = my_design))
conf
```

A 95% confidence interval is [`r conf[1]`, `r conf[2]`].

## Subtask 2 

### Calculate Mean by Branch

```{r test}
Employee.B.Branch%>%
  summarise(n= n(), Mean= mean(Total_of_Ratings),Var=sd(Total_of_Ratings)^2)

Employee.B.Branch%>% group_by(Branch)%>%
  summarise(n= n(), Mean= mean(Total_of_Ratings),StD=sd(Total_of_Ratings))
```

The estimated average rating for California is 4.391302, for HongKong is 4.164182, for Paris is 4.006737.

### Hypothesis Test
 
We perform a hypothesis test to determine whether there is evidence that any of the ratings are statistically significantly different from each other in the population.

$H_0 : {\mu}_{california}={\mu}_{hongkong}={\mu}_{paris}$

$H_1 : {\mu}_{california}\neq{\mu}_{hongkong}$ or ${\mu}_{california}\neq{\mu}_{paris}$ or 
${\mu}_{hongkong}\neq{\mu}_{paris}$ (i.e. the means are not all equal).

We perform an ANOVA.

```{r}
rating_aov = aov(Total_of_Ratings~Branch,data=Employee.B.Branch)
summary(rating_aov)
```

We obtain $p-value < 2.03e-07$ so $p-value < \alpha$. Therefore, we reject the null hypothesis and we conclude that there is evidence that Employee B could achieve more precision for these estimates.

## Subtask 3

For Employee A: 
Overall estimated average rating: 4.2227 
SE: 0.0125
95% confidence interval: [4.198217, 4.247116]
California estimated average: 4.396533
HongKong estimated average: 4.213475
Paris estimated average: 3.976963
Result of ANOVA: the means are not all equal

For Employee B: 
Overall estimated average rating: 4.2182 
SE: 0.0308
95% confidence interval: [4.157762, 4.278607]
California estimated average: 4.391302
HongKong estimated average: 4.164182
Paris estimated average: 4.006737
Result of ANOVA: the means are not all equal


